\section{The challenge with using sandboxing}
%
\Red{There's probably some punny covid title about sanitization we could include}

A somewhat commonly held belief is that actually enforcing memory isolation on a piece of code 
i.e. sandboxing it, presents the key challenge in this space.
%
This is not the case---sandboxing a piece of code, using software based checks has been solved 
at least for the last decade if not more.
%
However, when using a untrusted library that has been sandboxed, the problem you would 
eventually run into is ``how can I trust the output of a untrusted sandboxed library''.
%
While it is true, that the library has been sandboxed, nothing stops a compromised library from 
returning malformed data to the application.
%
In fact this data could malformed in a way to corrupt the application, get the application to 
leak its data and more; i.e. it could have the exact same impact as a buffer overflow in an 
unsandboxed library.

This area has perhaps received less attention than it should have in prior academic research.
%
This is not unreasonable---there are several interesting performance and scaling problems that 
are being closely studied and improved by academia.
%
However, this means that it is very common to some statement of the form ``In this paper, we 
assume that application developers have added checks that adequately sanitize all data received 
from the sandboxed library; addition of these checks are outside of the scope of this paper''. 
%
Unfortunately, we are still missing straightforward guidance on what these checks are and where 
they must be added.
%
Furthermore, a quick examination of usage patterns of some common libraries such as \jpeg, 
\png, \vorbis etc. reveal that (1) it is extremely challenging to ensure that all adequate 
safety checks have been added and (2) missing safety checks can relatively easily yield 
arbitrary read, write, or execute gadgets, ASLR breaks, information leaks etc.

Consider the example \todo{}.
%
A more detailed examination of such patterns is shown in \tocite{rlbox, two-worlds-sgx}.
